---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`natmed2`

[![Travis-CI Build Status](https://travis-ci.org/benkeser/natmed2.svg?branch=master)](https://travis-ci.org/benkeser/natmed2)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/benkeser/natmed2?branch=master&svg=true)](https://ci.appveyor.com/project/benkeser/natmed2)
[![Coverage Status](https://img.shields.io/codecov/c/github/benkeser/natmed2/master.svg)](https://codecov.io/github/benkeser/natmed2?branch=master)
[![MIT license](http://img.shields.io/badge/license-MIT-brightgreen.svg)](http://opensource.org/licenses/MIT)

> Multiply robust estimators of natural mediation parameters for designs where the measurement of the mediator is subject to two-phase sampling.

__Author:__ [David Benkeser](https://www.sph.emory.edu/faculty/profile/#!dbenkes)

---

## Description

`natmed2` is an R package that computes multiply robust estimators of natural mediation effects in settings where the mediator is measured subject to two-phase sampling. 

---

## Installation

<!-- 
Install the current stable release from
[CRAN](https://cran.r-project.org/) via

```{r cran-installation, eval = FALSE}
install.packages("natmed2")
```
 -->

A developmental release may be installed from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/) with:

```{r gh-installation, eval = FALSE}
devtools::install_github("benkeser/natmed2")
```

---

## Usage

Below is an illustration of the the main function on simulated data. 


```{r, sim-data}
n <- 500
W1 <- rbinom(n, 1, 0.5)
W2 <- rnorm(n, 0, 1)
A <- rbinom(n, 1, 0.5)
S <- W1 / 4 - W2 / 3 + A + rnorm(n)
Y <- rbinom(n, 1, plogis(-2 + A + W1 / 2 - S / 2))

# add censoring
C <- rbinom(n, 1, plogis(2 + W1 / 2 - W2 / 3))
# arbitrary fill in
Y[C == 0] <- -999

R <- rep(0, n)
# case-cohort sampling
R <- rbinom(n, 1, 0.25)
R[Y == 1] <- 1

library(natmed2)
fit <- natmed2(
  W = data.frame(W1 = W1, W2 = W2), 
  A = A, R = R, S = S, C = C, Y = Y
)

fit
```

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/benkeser/natmed2/issues).

---

## License

&copy; 2016-2019 [David C. Benkeser](https://www.sph.emory.edu/faculty/profile/#!dbenkes)

The contents of this repository are distributed under the MIT license. See
below for details:
```
The MIT License (MIT)

Copyright (c) 2016-2019 David C. Benkeser

Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all
copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.
```
